### 2016-06-24 sec5_spm-bk.tex
An almost finished version
Continue to revise

\section{SPARE: Star Partitioning and Apriori Enumerator}
\label{sec:spm}
The aforementioned replicate partitioning is based on the temporal dimension which suffers from two drawbacks. First, the replication relies on $\eta$ which could be large. Second, the same valid pattern may be discovered from different partitions which results in redundant work.
%and results in groups of snapshots in each partition.
% ADD MORE DETAILS ABOUT THE LIMITATIONS HERE.
To resolve the limitations caused by the replicate partitioning, 
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second cycle of map-reduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
contains all the valid GCMP patterns. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

@@

\subsubsection{Apriori Enumeration}
We then design the Apriori enumeration method to
systematically discover all valid patterns in a star.
%During the enumeration, we refer a candidate pattern
%$P$ as a $R$-candidate if $|P.O|=R$.
The enumeration method discover patterns iteratively using ``bottom-up'' order:
candidates with smaller objects set grow one object per iteration.
%
%in iteration $i$,  all $(i+1)$-candidates grows
%to $(i+2)$-candidates.
%
Enumeration ends if no
further candidates can be generated.

 Due the \emph{monotonicity} proved in Theorem~\ref{THM:SPARE_MONO}, we are able to use the \emph{monotonic pruning} and \emph{forward closure check} to boost the enumeration process. We show the detail of the process
in Algorithm~\ref{algo:apriori_mining}. As a start, 
each input edge is treated as a candidate pattern, with the 
inverted list as the time sequence. These candidates
are kept in $\mathbf{G}$ as the ground set (Lines~\ref{code:init-start}-\ref{code:init-end}). In initialization, the inverted lists are simplified (Line~\ref{code:simp1}) and unqualified lists are pruned (Line~\ref{code:init-prune}). Throughout the algorithm, we maintain a set of candidates $\mathbf{C}$ which is initialized to the ground set $\mathbf{G}$ (Line~\ref{code:init-C}).

In each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}),  the members in candidate set are joined with the members in ground set to generate new candidates (Lines~\ref{code:join-start}-\ref{code:join-ends}). The join of two candidates $c$ and $g$ creates a 
new candidate, whose objects are the union of $c.O$ and$g.O$ and the time sequence is the intersection of $c.T$ and $g.T$ (Line~\ref{code:join}). During the join,
we use \emph{sequence simplification} to detect unqualified candidates. By \emph{monotonicity}, these candidates are safely excluded from the future iterations~(Line~\ref{code:mono-pruning}). If a valid candidate is not able to be extended by any ground set, we directly output it (Line~\ref{code:output1}).

After the join finishes, we start a \emph{forward closure} check (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-ends}). We test whether the union of all candidates in $\mathbf{C}$ forms a valid pattern. If the check succeeds, we output such union and stop the iteration~(Lines~\ref{code:fc-checking}).

\eat{
to union all the candidates in the current candidate set, and quickly check whether the

To systematically discover valid patterns in each star,

we enumerate all valid patterns in ``bottom-up" order: 
pattern candidates with smallest object sizes are enumerated
first and grew to pattern candidates with larger object sizes.
During the enumeration, we call a candidate pattern
$P$ a $R$-pattern, if $|P.O|=R$.  The enumerator takes
a star as input, and treat each edge as a $2$-pattern.

The input of
the enumerator is a star. Each edge
in the star is treated a $2$-candidate, with the inverted
list to be the time sequence.

we design the \emph{Apriori Mining} algorithm. We borrow
the terminologies in classic Aprirori algorithm: a candidate
pattern $P$ is called $R$-pattern if the $|P.O|=R$. In Aprirori,
candidates grows from $2$-pattern level by level.

To describe the algorithm, we call a candidate pattern $R$-pattern 
if the size of its object set is $R$.  Therefore, each edge
in the star is effectively a $2$-pattern. The intuition of Apriori mining
is the observation that $(R+1)$-patterns can be generated
from $R$-patterns and $2$ patterns. Thus, we may iteratively 
enumerate pattern candidates with all possible sizes.
In particular, initially, for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. 
During each iteration, we generate $(R+1)$-patterns by joining $R$-patterns 
with the $2$-patterns. Technically, the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$
generates a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Note that in $Sr_s$,
each $R$-pattern contains the object $s$, thus the join only 
grow a $R$-pattern at most to a $(R+1)$-pattern.
Our mining algorithm stops where no further patterns are generated. 
The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.
}

\begin{algorithm}
\caption{Apriori Enumerator}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State {$\mathbf{C} \gets \{\}$, $\mathbf{G} \gets \{\}$, $\mathbf{OT} \gets \{\}$}
\ForAll{$e(s,t) = T \in Sr_s$} \label{code:init-start}
\State {$T' \gets \mathtt{sim}(e(s,t))$} \label{code:simp1}
\State {$\mathbf{G}.\mathtt{add}(\langle \{s,t\}: T' \rangle)$, unless $T' \neq \emptyset$}\label{code:init-prune}
\EndFor\label{code:init-end}
\State {$\mathbf{C} \gets \mathbf{G}$}\label{code:init-C}
\While{$\mathbf{C} \neq \emptyset$} \label{code:level-start}
		\State {$\mathbf{N} \gets \{\}$, $U \gets \{\}$}
		\ForAll{$(c,g)\in \mathbf{C}$} \label{code:join-start}
			\ForAll {$g \in \mathbf{G}$}		
				\State {$c' \gets \langle c.O \cup g.O: \mathtt{sim}(c.T \cap g.T )\rangle$} \label{code:join}
				\State {$\mathbf{N}$.add$(c')$, unless $c'.T \neq \emptyset$} \label{code:mono-pruning}
			\EndFor
			\State $\mathbf{OT}$.add$(c)$, if $c$ is not extended.\label{code:output1}
		\EndFor	\label{code:join-ends}
		\State {$\mathbf{C} \gets \mathbf{N}$}
		\State $U \gets $ union of $n_i \in \mathbf{C}$	\label{code:fc-checking-start}
		\If {$U$ is a valid pattern}
			\State $\mathbf{Output}.\mathbf{add}(U)$ \label{code:fc-checking}
			\State break;
		\EndIf \label{code:fc-checking-ends}
\EndWhile\label{code:level-ends}
\State $\mathbf{OT}$.addAll$(\mathbf{C})$
\State \Return $\mathbf{OT}$
\end{algorithmic}
\end{algorithm}

%An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
%As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
%higher level candidates are generated by joining lower level candidates. When no more candidates 
%can be generated, the algorithm stops by outputting the valid patterns.
%

\begin{example}
We use Figure~\ref{fig:star_partition} (c) to 
demonstrate the power of candidate pruning. 
As shown, at the initial stage, $\{3,6:3\}$ is first pruned by \textit{simplification}. 
Subsequently, all further candidates containing $\{3,6\}$ 
are pruned by \textit{Monotonicity}. Then, we check the \textit{Forward Closure} 
of remaining candidates (i.e., $\{3,4\}$ and $\{3,5\}$) and find $\{3,4,5\}$ is a
valid candidate. Therefore, $\{3,4\}$ and $\{3,5\}$ are pruned, and $\{3,4,5\}$ is the output.
\end{example}

%
%It is notable that, in star partition, original data is 
%replicated at most $O(|\mathbb{O}|)$ times.
%In later sections, we will describe several 
%more optimization techniques to further reduce the amount of replicated data.

%In such a way, 
%given an object $u$, all the objects potentially
%co-moved with $u$ are captured in $u$'s neighborhood, which
%forms a \emph{star} structure in graph terms. SPM utilizes
%such structures to partition objects and then adapts an Apriori 
%algorithm to discover true GCMPs from each partition.

\eat{

EXPLAIN CLEARLY HOW YOU IMPLEMENT THE FORWARD CLOSURE CHECKING! BETTER SHOW IT IN THE ABOVE PSEDUDO CODE IN THE APRIORI ALGORITHM.

Although leveraging \emph{temporal monotonicity} could largely prune
false candidates and reduce the apriori search space, 
it is ineffective when a \textit{true} pattern exists. 
In an extreme case, if a final pattern of a star $Sr_s$ is 
the \textit{union of all vertices} in the star,
then in apriori, ${|Sr_s|}\choose{i + 1}$ candidates needs to be generated at 
each level $i$. This results in an exponential search space while
the output only contains one pattern.  
Generally, when candidates at level $i$ collectively forms a true pattern, 
running aprior produces many wasted candidates.

Let $Lv_i$ be the set of candidates at level $i$ of Algorithm~\ref{algo:apriori_mining},
we use the \emph{forward closure} $FC_i$ to denote the union of the objects in
all candidates in $Lv_i$. Then, the \emph{forward closure checking} is stated as follows:
\begin{theorem}[Forward Closure Checking]
\label{THM:SPM_FCC}
Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
and directly output $FC_i$.
\end{theorem}

It is notable that, as the level grows in Algorithm~\ref{algo:apriori_mining}, the closure $FC$
reduces, thus the terminating power of $FC$ would be stronger. We give hybrid example of the three
optimization as follows:
%To facilitate efficient mining, we adapt the \emph{forward closure checking} rule to 
%quickly determine whether it is sufficient to terminate the apriori search. Given the candidates at
%level $i$ $Lv_i$, we define the \emph{forward closure} of $Lv_i$ as the union of objects from
%all candidates. Then, the following \emph{forward closure checking} rule can be used:
%
%\begin{theorem}[Forward Closure Checking Rule]
%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining}, the forward closure
%is $\mathbb{F}_i = \cup_{cand \in Lv_i} (cand.O) $. Algorithm~\ref{algo:apriori_mining} terminates when 
%$FC_i$ forms a valid GCMP .
%\end{theorem}
}

\subsection{Put It Together}
With the star partition and the Apriori enumerator, we are ready to assemble the Star Partition and ApRiori Enumerator (SPARE) framework. 
We summarize the workflow of SPARE in Figure~\ref{fig:star_partition} as follows: After the parallel clustering in each snapshot, we build an aggregated graph $G_A$ to capture the clustering relationship. In the map phrase, we partition $G_A$ into stars and emit the star partitions to the reducers. Each reducer is an Apriori Enumerator. When receiving a star $Sr_i$, the reducer creates initial candidate patterns. Specifically, for each $o \in Sr_i$, a pattern candidate $\{o,i: e(o,i)\}$ is created. Then it enumerates all true patterns from the candidate patterns. The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}. Note that we do not need to create an actual aggregate graph. Instead, we only to emitted the directed edges (Line~\ref{code:spm-edge-direct}).

\begin{algorithm}
\caption{Star Partition and ApRiori Enumerator}
\label{algo:spm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State {---Map phase---}
\label{code:spm-map-start}
\ForAll{$C \in S_t$}
	\ForAll {$(o_1 ,o_2) \in C \times C$}
	\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet, if $o_1 < o_2$~\label{code:spm-edge-direct}
	\EndFor
\EndFor
\label{code:spm-map-end}

@@

Our SPARE framework does not rely on the pattern parameters to determine the partition size,
which is more stable than TRMP. In addition, we observe that the patterns mined from each
reducer are unique. This property is stated as follows:
\begin{theorem}[Pattern Uniqueness]
\label{LEM:SPM_CORRECT}
Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \not\equiv p_j.O$.
\end{theorem}
\begin{proof}
We prove by contradiction. Suppose exists $p_i \in P_i$ and $p_j \in P_j$ s.t. $p_i.O \equiv p_j.O$.
Let $o_i$ (resp. $o_j$) be the object with smallest ID in $p_i.O$ (resp. $p_j.O$).
Since $p_i$ and $p_j$ belongs to different stars, then $o_i \neq o_j$,  which contradicts with
the assumption $p_i.O \not\equiv p_j.O$. 
\end{proof}

Theorem~\ref{LEM:SPM_CORRECT} confirms the superiority of SPARE to TRPM. In TRPM, a pattern
may be repeatedly discovered from different partitions, while in SPARE a pattern is only discovered once. This suggests that SPARE require less redundant works. We finally conclude this section with the following theorem:

\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}
See Appendix XXXX.
\end{proof}

\eat{ \subsection{Correctness of SPARE}
We summarize the workflow of SPARE framework in Figure~\ref{fig:star_partition} as follows. After the parallel clustering in each snapshot, we build an aggregated graph $G_A$ to capture the clustering relationship. In the map phrase, we partition $G_A$ into stars and emit the star partitions to the reducers. Each reducer is an Apriori Enumerator. When receiving a star $Sr_i$, the reducer creates initial candidate patterns. Specifically, for each $o \in Sr_i$, a pattern candidate $\{o,i: e(o,i)\}$ is created. Then the Apriori algorithm enumerate the true patterns from the candidate patterns. Meanwhile, the \emph{simplification}, \emph{monotonicity pruning} and \emph{forward closure checking} are applied to boost the enumeration process.
ADD THE DETAILS WHEN THE REDUCER RECEIVE THE STAR PARTITIONS. HOW THEY DERIVE THE FINAL RESULT PATTERNS.

\eat{
\begin{algorithm}
\caption{Star Partition and Mining}
\label{algo:spm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State {---Map phase---}
\label{code:spm-map-start}
\ForAll{$C \in S_t$}
	\ForAll {$(o_1 ,o_2) \in C \times C$}
		\If{$o_1 < o_2$}  \label{code:spm-edge-direct}
			\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet
		\EndIf
	\EndFor
\EndFor
\label{code:spm-map-end}

\State {---Reduce phase---}
\label{code:spm-reduce-start}
\ForAll{$\langle o, Sr_{o} \rangle$}
\State Apriori($Sr_o$)
\EndFor
\label{code:spm-reduce-end}

\end{algorithmic}
\end{algorithm}
}

In the following, we show the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}
If $P$ is a valid pattern in original trajectories, 
let $s$ be the object with smallest ID in $P.O$. 
Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
It follows that all object $o \in P.O$ are in $Sr_s$. 
Furthermore, every timestamp in $P.T$ is included
in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$. This ensures the \emph{completeness}. For any pattern $P$ enumerated by SPARE, by definition of star partition, $\forall o_1, o_2 \in P.O$, $\forall t \in P.T$, $C_t(o_1) = C_t(o_2)$. This ensure the \emph{soundness}.
\end{proof}

In fact, besides that every valid patterns can be
mined in some stars, star partition further ensures
that patterns discovered
from different star partitions cannot be the same. 
This can be formulated as:

\eat{It is also interesting to observe that no duplicate patterns will be generated from the star partitions.}
\begin{lemma}[Pattern Uniqueness of Star Partition]
\label{LEM:SPM_CORRECT}
Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \not\equiv p_j.O$.
\end{lemma}
\begin{proof}
The correctness of Lemma~\ref{LEM:SPM_CORRECT} can be directly derived from the above arguments:
let $o_i$ be the smallest element in $p_i.O$ and $o_j$ be the smallest element in $p_j.O$. 
Since $p_i$ and $p_j$ belongs to different stars, then $o_i \neq o_j$, 
therefore $p_i.O \not\equiv p_j.O$. This proves the lemma.
\end{proof}

This lemma verifies the superiority of the SPARE framework over the TRPM framework.
}

>>>>

\section{SPARE: Star Partitioning and Apriori Enumerator}
\label{sec:spm}
The aforementioned replicate partitioning is based on the temporal dimension which suffers from two drawbacks. First, the replication relies on $\eta$ which could be large. Second, the same valid pattern may be discovered from different partitions which results in redundant works.
%and results in groups of snapshots in each partition.
% ADD MORE DETAILS ABOUT THE LIMITATIONS HERE.
To resolve the limitations caused by the replicate partitioning, 
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second cycle of map-reduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
contains all the valid GCMP patterns. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

@@

\subsubsection{Apriori Enumeration}
We design an Apriori enumeration method to efficiently discover all the valid patterns in a star partition. The principle of Apriori algorithm is to construct a lattice structure and enumerate all the possible candidate sets in a bottom-up manner. Its merit lies in the monotonic property such that if a candidate set is not valid, then all its supersets can be pruned. Thus, it works well in practice in spite of the exponential search space.

Our customized Apriori Enumerator is presented in Algorithm~\ref{algo:apriori_mining}. Initially, the edges (pairs of objects) in the star constitute the bottom level (Lines~\ref{code:init-start}-\ref{code:init-end}) and unqualified candidates are excluded (Line~\ref{code:simp1}). A indicator \emph{level} is used to control the object size of the current candidates. During each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}), only candidates with object size equals to \emph{level} are generated (Line~\ref{code:join-start}). When two candidate sets $c_1$ and $c_2$ are joined, the new candidate becomes $c'=\langle c_1.O \cup c_2.O, c_1.T\cap c_2.T\rangle$ (Lines~\ref{code:join}). To check the validity of the candidate, we calculate $\mathtt{sim}(c'.T)$. If its simplified sequence is empty, $c'$ is excluded from the next level (Line~\ref{code:simp2}). This ensures that
then all the candidates with $P.O\supseteq c'.O$ are excluded. If a candidate cannot generate any new candidates, then it is directly outputted (Lines~\ref{code:output1-start}-\ref{code:output1-end}).
To further improve the performance, we adopt the idea of \textit{forward closure}~\cite{wang2003closet+,pei2000closet} and  aggressively check if the union of all the current candidates form a valid pattern (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-end}). If yes, we can early terminate the algorithm and output the results.

\begin{algorithm}
\caption{Apriori Enumerator}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State {$C \leftarrow \emptyset$}
\ForAll{edges $c=\langle o_i\cup o_j, T_{o_i}\cap T_{o_j}\rangle$ in $Sr_s$} \label{code:init-start}
\If {$\mathtt{sim}(T_{o_i}\cap T_{o_j})\neq \emptyset$}
\State {$C\leftarrow C\cup \{c\}$} \label{code:simp1}
%\ElsIf{$c$ is a valid pattern}
%\State{output $c$}
\EndIf 
\EndFor\label{code:init-end}
\State $\mathrm{level} \gets 2$ \label{code:level}
\While{$C\neq \emptyset$} \label{code:level-start}
	\ForAll{$c_1 \in C$}
		\ForAll{$c_2 \in C$ and $|c_2.O \cup c_2.O| = \mathrm{level}$}\label{code:join-start}	
			\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}			
			\If{ $\mathtt{sim}(c'.T)\neq \emptyset$} \label{code:simp2}
					\State {$C'\leftarrow C'\cup \{c'\}$}
			\EndIf			
		\EndFor\label{code:join-end}
		\If {no $c'$ is added to $C'$} \label{code:output1-start}
			\If{$c_1$ is a valid pattern}
				\State output $c_1$
			\EndIf
		\EndIf \label{code:output1-end}
	\EndFor
%	
%		\ForAll{pairs $c_1\in C$, $c_2\in C$ and $c_1\neq c_2$} \label{code:join-start}
%				\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}
%				\If{ $\mathtt{sim}(c_1.T \cap c_2.T )\neq \emptyset$}
%					\State {$C'\leftarrow C'\cup \{c'\}$}
%					\ElsIf{$c'$ is a valid pattern}
%						\State{output $c'$}
%				\EndIf
%		\EndFor	\label{code:join-ends}
	\State $O_u \gets $ union of $c.O$ in $C$	\label{code:fc-checking-start}
	\State $T_u \gets $ intersection of $c.T$ in $C$	
	\If {$\langle O_u, T_u\rangle$ is a valid pattern}
		\State{output $\langle O_u, T_u\rangle$} \label{code:fc-checking}
		\State break;
	\EndIf \label{code:fc-checking-end}
	\State {$C\leftarrow C';C'\leftarrow \emptyset; \mathrm{level} \gets \mathrm{level}+1$}	
\EndWhile\label{code:level-ends}
\State output $C$ \label{code:output2-end}
\end{algorithmic}
\end{algorithm}

\begin{example}
As shown in Figure~\ref{fig:star_partition}(c), in the bottom level of the lattice structure, candidate $\{3,6:3\}$ is pruned because its simplified sequence is empty. Thus, all the object sets containing $\{3,6\}$ can be pruned. The remaining two candidates (i.e., $\{3,4:1,2,3\}$ and $\{3,5:2,3\}$)  derive a new  $\{3,4,5:2,3\}$ which is valid. By the forward closure checking, the algorithm can terminate and output $\{3,4,5:2,3\}$ as the final closed pattern.
\end{example}

\subsection{Put It Together}
We summarize the workflow of SPARE in Figure~\ref{fig:star_partition} as follows. After the parallel clustering in each snapshot, for ease of presentation, we used an aggregated graph $G_A$ to capture the clustering relationship. However, in the implementation of the map phrase, there is no need to create $G_A$ in advance.  Instead, we simply need to emit the edges within a star partition to the same reducer.  Each reducer is an Apriori Enumerator. When receiving a star $Sr_i$, the reducer creates initial candidate patterns. Specifically, for each $o \in Sr_i$, a candidate pattern $\{o,i: e(o,i)\}$ is created. Then it enumerates all the valid patterns from the candidate patterns. The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}.

\begin{algorithm}
\caption{Star Partition and ApRiori Enumerator}
\label{algo:spm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State {---Map phase---}
\label{code:spm-map-start}
\ForAll{$C \in S_t$}
	\ForAll {$o_1 \in C,  o_2 \in C, o_1 < o_2$}
	\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet~\label{code:spm-edge-direct}
	\EndFor
\EndFor
\label{code:spm-map-end}

@@

Compared with TPMP, the SPARE framework does not rely on snapshot replication to guarantee correctness. In addition, we can show that the patterns derived from a star partition are unique and there would not be duplicate patterns mined from different star partitions.
\begin{theorem}[Pattern Uniqueness]
\label{LEM:SPM_CORRECT}
Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \neq p_j.O$.
\end{theorem}
\begin{proof}
We prove by contradiction. Suppose there exist $p_i \in P_i$ and $p_j \in P_j$ with the same object set. Note that the center vertex of the star is associated with the minimum id. Let $o_i$ and $o_j$ be the center vertices of the two partitions and we have $o_i=o_j$. However, $P_i$ and $P_j$ are different stars, meaning their center vertices are different (i.e., $o_i\neq o_j$), leading to a contradiction. 
\end{proof}

Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
%that no replication is required 
in the SPARE framework, which is superior to the TRPM baseline. Finally, we prove the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}
See Appendix XXXX.
\end{proof}
